A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-21 paper/ms.tex
update ms for RM discussion

% gaia target sample numbers
\newcommand{\nkinematic}{1{,}201} % deltalyr_kc19_cleansubset_withreddening.csv
% all from oneoff_calculate_rotation_numbers.py
\newcommand{\noriginal}{3{,}071} % Vizier; KC19 Theia 73 member count
\newcommand{\nwithtess}{924} % How many stars have TESS data?
\newcommand{\nkinwithtess}{391} % How many kinematically selected stars have TESS data?
\newcommand{\nkinwithtessandcrowding}{192} % How many kinematically selected stars have TESS data and meeting the crowding cutoff (nequal<=0, nclose<=1)?
\newcommand{\nkindefaultcleaning}{145} % How many of these meet the "defaultcleaning" criteria (LSP>0.1, Prot<15, and crowding cut)?
\newcommand{\nrotgood}{135} % nkindefaultcleaning, minus outliers.
\newcommand{\nfracprot}{70} % fraction nrotgood/nkinwithtessandcrowding

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster, based on Gaia kinematics, TESS stellar rotation periods,
  and spectroscopic lithium abundances.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  From unresolved starspot-crossing
  events in the Kepler photometry and a Keck/HIRES transit we find
  that the planet is likely on an orbit aligned with the stellar spin
  axis.  We also briefly explore the flare arrival time distribution
  in the short cadence Kepler photometry.  The $\delta$~Lyr cluster is
  one of many stellar groups whose properties have been clarified
  using Gaia; many other new clusters also overlap with confirmed and
  candidate exoplanets.  Verifying the results of Gaia clustering
  analyses using TESS rotation periods offers a promising path toward
  expanding the census of age-dated planets, and our corresponding
  understanding of planetary evolution.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open
clusters were known in the Kepler field: NGC\,6866, NGC\,6811,
NGC\,6819, and NGC\,6791, with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Since that time, analyses of the
kinematic, photometric, and astrometric Gaia data have expanded our
knowledge of open cluster and moving group memberships \citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The
candidate \cn\ members shown are
selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical method
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and manually excluded stars that
were obvious photometric binaries in the CAMD.  We then passed a moving
box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, TESS data were available for
\nwithtess\ stars.\footnote{Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 56 stars; in these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (1 TESS pixel).  We recorded the
number of stars within the aperture with greater brightness than the
target star, and with brightness within 1.25 and 2.5 TESS magnitudes
of the target star.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.
The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}. 
Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
noted in the literature.

@@

In summary, the age of the \cn\ based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have
not yet converged to a slow sequence, their rotation periods 
are generally consistent with an $\approx$38\,Myr age. The most
precise age for \sn\ and its planet are therefore identical to the cluster,
based on the star's spatial and kinematic association with the
cluster, and the assumption that the planet formed shortly after
the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[see {\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 2021 March 26 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the
effective temperature of \sn\ (Table~\ref{tab:starparams}), this
measurement is also in line with expectations for a $\approx$38\,Myr
star ({\it e.g.}, \citealt{randich_gaiaeso_2018};
\citealt{bouma_2021_ngc2516}).

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the spectroscopic detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting
			exoplanets}.  Planets older than $10^9$ years are shown with gray
		markers.  Planets younger than a gigayear with ${\rm
			\tau}/\sigma_{\rm \tau} > 3$ are emphasized, for $\tau$ the age.
		\pn\ is shown with a
		star.  The large sizes of the youngest transiting planets could be
		explained by their primordial atmospheres not yet having
		evaporated; direct measurements of the atmospheric outflows or
		planetary masses would help to confirm this expectation.
		Selection effects may also be important.  Parameters are from the
		NASA Exoplanet Archive (2021 Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

There are three new lines of evidence that support the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is
$\approx 4.6\,{\rm g\,cm}^{-3}$ (Table~\ref{tab:posterior};
\citealt{choi_mesa_2016}).  The transit duration is therefore too long
to be explained by a star eclipsing the M dwarf secondary at
$10$-$\sigma$.

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the
144 observed transits to within $\pm4.5$\,hr of each transit, and
fitted each window with both {\it i)} a local second-order polynomial
and transit, and {\it ii)} a local linear trend.  We let the mid-time
of each transit float, and then calculated the residual between the
measured mid-time and that of a periodic orbit.  This
residual, the transit timing variation (TTV), is plotted in
Figure~\ref{fig:obliquity} against the local linear slope.  A
significant correlation of $-0.0564 \pm 0.0098\ {\rm ppt\,day}^{-1}$
is observed.  Less than ten Kepler Objects of Interest have shown this
correlation \citep{holczer_time_2015}, which is most readily
interpreted as a TTV induced by unresolved starspot crossings
\citep{mazeh_time_2015}.  This is only possible if the planet transits
the primary star, which excludes a background eclipsing binary
scenario, and therefore confirms that \pn\ is a planet.  It also
implies that the planet's orbit is prograde.  The latter
interpretation assumes that the dominant photometric variability is
induced by dark spots, rather than bright faculae
\citep{mazeh_time_2015}.  Given the observed transition of Sun-like
stellar variability from spot to faculae-dominated regimes, we expect
this inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 2021 Aug 7.  We
used the iodine cell for wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

% from /drivers/logs/rm.log
% quad: 
% chi2red: 4.452
% BIC: 272.434
% AIC: 264.796
%
% linear:
% chi2red: 5.425
% BIC: 291.987
% AIC: 285.441
%
% trendonly:
% chi2red: 4.256
% BIC: 274.383
% AIC: 270.018
%
% retrograde:
% chi2red: 5.439
% BIC: 292.415
% AIC: 285.869
% 
% prograde:
% chi2red: 4.320
% BIC: 272.039
% AIC: 265.493

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, 
following the methodology developed by \citet{stefansson_2020}.
We allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary, and fixed the limb-darkening
using the $V$-band tabulation from \citet{claret_gravity_2011}.  We also
allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorporated.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Comparing the expected semi-amplitude of the velocity anomaly
for a well-aligned orbit ($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) with the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

>>>>

% gaia target sample numbers
\newcommand{\nkinematic}{1{,}201} % deltalyr_kc19_cleansubset_withreddening.csv
% all from oneoff_calculate_rotation_numbers.py
\newcommand{\noriginal}{3{,}071} % Vizier; KC19 Theia 73 member count
\newcommand{\nwithtess}{924} % How many stars have TESS data with G<17 and (Bp-Rp)0 > 0.5?
\newcommand{\nforgyro}{1842} % How many stars have G<17 and (Bp-Rp)0 > 0.5?
\newcommand{\nkinwithtess}{391} % How many kinematically selected stars have TESS data?
\newcommand{\nkinwithtessandcrowding}{192} % How many kinematically selected stars have TESS data and meeting the crowding cutoff (nequal<=0, nclose<=1)?
\newcommand{\nkindefaultcleaning}{145} % How many of these meet the "defaultcleaning" criteria (LSP>0.1, Prot<15, and crowding cut)?
\newcommand{\nrotgood}{135} % nkindefaultcleaning, minus outliers.
\newcommand{\nfracprot}{70} % fraction nrotgood/nkinwithtessandcrowding

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  From unresolved starspot-crossing
  events in the Kepler photometry and a Keck/HIRES transit we find
  that the planet is likely on an orbit aligned with the stellar spin
  axis.  We also briefly explore the flare arrival time distribution
  in the short cadence Kepler photometry.  The $\delta$~Lyr cluster is
  one of many stellar groups whose properties have been clarified
  using Gaia; many other new clusters overlap with confirmed and
  candidate exoplanets.  Verifying the results of Gaia clustering
  analyses using TESS rotation periods offers a promising path toward
  expanding the census of age-dated planets, and our corresponding
  understanding of planetary evolution.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open
clusters were known in the Kepler field: NGC\,6866, NGC\,6811,
NGC\,6819, and NGC\,6791, with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Since that time, analyses of the
kinematic, photometric, and astrometric Gaia data have expanded our
knowledge of open cluster and moving group memberships \citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of stars in the \cn, IC\,2602, the Pleiades, and the
field.  The candidate \cn\ members shown are selected based on their
positions and kinematics (see Appendix~\ref{app:kinematicselection}).
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 = 3.1
E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{damiani_stellar_2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
manually excluded stars that were obvious photometric binaries in the
CAMD.  We then passed a moving box average and standard deviation
across the CAMD in 0.10\,mag bins, fitted a univariate spline to the
binned values, and assembled a piecewise grid of hybrid isochrones
spanning the ages between UCL to the Pleiades using Equations~6 and~7
from \citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } While detailed analyses of the LDB or
main-sequence turn-off in the \cn\ could help resolve the tension
between the LDB and isochrone ages, these are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, \nwithtess\ stars were amenable to
rotation period measurements ($G<17$ and $\bpmrpo>0.5$) and had TESS
data available.\footnote{Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 56 stars; in these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (1 TESS pixel).  We recorded the
number of stars within the aperture with greater brightness than the
target star, and with brightness within 1.25 and 2.5 TESS magnitudes
of the target star.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.  The
rotation period distributions of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  Binarity is known to be an
important factor in the density of stars falling underneath the slow
sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those previously noted in the
literature.

@@

To summarize, the age of the \cn\ based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have not
yet converged to a slow sequence, their rotation periods are generally
consistent with a 38\,Myr age. The most precise age for \sn\ and its
planet are therefore identical to the cluster, based on the star's
spatial and kinematic association with the cluster, and the assumption
that the planet formed shortly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[{\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 2021 March 26 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   %Note that this value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA. 
Given the effective temperature of \sn\ (Table~\ref{tab:starparams}),
this measurement is also in line with expectations for a 38\,Myr star
({\it e.g.}, \citealt{randich_gaiaeso_2018};
\citealt{bouma_2021_ngc2516}).

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux changes by
    $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3.
    The best-fit sky-projected obliquity for this model is listed in
    red.  While the intra-exposure RV scatter precludes a detection of
    the RM effect, the photometric transit depths are consistent
    across the {\it griz} bandpasses.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets older than $10^9$ years are shown with gray markers.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\rm \tau}
    > 3$ are emphasized, for $\tau$ the age.  \pn\ is shown with a
    star.  The large sizes of the youngest transiting planets could be
    explained by their primordial atmospheres not yet having
    evaporated; direct measurements of the atmospheric outflows or
    planetary masses would help to confirm this expectation.
    Selection effects may also be important.  Parameters are from the
    NASA Exoplanet Archive (2021 Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

There are two new lines of evidence that confirm the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:obliquity}
against the local linear slope.  A significant correlation of $-0.0564
\pm 0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Less than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also implies that the planet's
orbit is prograde.  The latter interpretation assumes that the
dominant photometric variability is induced by dark spots, rather than
bright faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes, we expect this
inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit, and it appears to be achromatic
(Figure~\ref{fig:obliquity}, lower panels).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across
bandpasses, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The MuSCAT3
observations also suggest a transit duration $17.4\pm3.6\,{\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether such changes are indeed
happening.  For the RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While our RM data are marginally more
consistent with a prograde or polar orbit than a retrograde orbit,
given that the expected velocity anomaly ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$) is a factor of two smaller than the
spot-corrected exposure-to-exposure scatter, we are not in a position
to claim a spectroscopic detection of the RM effect, nor a precise
quantification of the stellar obliquity.
